### 2016-05-13 paper/figures.tex
add data and figure

>>>>

\newcommand{\FigEval}{
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.9\linewidth]{../data/times.pdf}
    \caption{\textbf{DDoSCoin effect}\,--\, %
    We set up a quad-core nginx HTTPS server on a local network, and used Apache
benchmark (ab) to measure page load times under normal conditions (no DDoSCoin
miner running) and with a single DDoSCoin instance. DDoSCoin increases the
average page-load time 6-fold from 43ms to over 291ms.}
    \label{fig:eval}
\end{figure}
}

### 2016-05-13 paper/paper.tex
add data and figure

To evaluate its performance, we implement our proof-of-DDoS function in 570
lines of C. Our mining code uses libevent~\cite{libevent} and
OpenSSL~\cite{openssl}.

From wifi: 100 concurrent conns, 10k connections total in 53 seconds, 500KB/s
roughly (no CPU load)

TODO: measure from CU...or to a local server?

\section{Discussion}

@@

\subsection{Defenses}

>>>>

\FigEval

To evaluate the performance and effectiveness of DDoSCoin, we implement our
proof-of-DDoS function in 582 lines of C. Our mining code uses
libevent~\cite{libevent} and OpenSSL~\cite{openssl} to create concurrent
connections toward a specific target, testing each response to see if it
satisfies a hard-coded proof-of-DDoS target difficulty.

We tested our proof-of-DDoS function (miner) against a quad-core server under
our control, running nginx and connected to our attacker over a local Gigibit
network. When running our miner, the CPU consumption of the server quickly
reaches 100\% utilization on all 4 cores, while the attacker only requires
approximately 30\% on a single core. This produces over 3000 TLS connections per
second, and slowing responses to the server by more than a factor of 6 (see
Figure~\ref{fig:eval}).

\if0
\section{Discussion}

@@

\subsection{Defenses}
\fi
\section{Defenses}
